What does the crowd believe? A hierarchical approach to estimating subjective beliefs from empirical data

### 2016-01-31 text/01_CogSci_abstract/paper.tex

Another possibility is to empirically measure subjective beliefs by ``give-a-number''
tasks. The simplest version would be this: being told that John just bought a new watch,
subjects are asked for a single numerical estimate of its price. This task is easy to
comprehend and implement, but a single number does not provide much information about the
subjective belief that it is (arguably) a manifestation of. One solution is to infer which
parameterized distribution best explains the observed number choices, either at the individual
level \citep{Manski2004:Measuring-Expec} or on the population level
\citep{TauberSteyvers2013:Inferring-Subje}.

More sophisticated ``give-a-number'' tasks give more information, but can be rather complex and
more difficult to implement. A prominent method in economics uses \emph{scoring rules}
\citep{Savage1971:Elicitation-of-,AndersenFountain2014:Estimating-Subj,SchlagTremewan2014:A-penny-for-you}. Roughly
put, scoring rules are schemes of rewarding participants' answers that make sure that responses
(by rational subjects) faithfully reflect a measure of interest: the actual subjective
probability of an event, the mean of a distribution, a credible interval etc. Scoring-rule
tasks require participants to become sufficiently familiar with the (usually probabilistic)
payoff scheme. Another insightful, but also complex approach is to use a cleverly designed
\emph{iterated learning paradigm} \citep{LewandowskyGriffiths2009:The-Wisdom-of-I}.

@@

A simple technique that seems to fit this bill is the \emph{binned histograms} task that has
recently been used with apparent success
\citep{KaoWu2014:Nonliteral-Unde,SchollerFranke2015:Semantic-values}. \mf{someone please add
  references: where did you use binned sliders?} Participants adjust sliders in order to
express their (relative) subjective beliefs about how likely it is that the value of an
uncertain contiguous quantity lies in some interval of possible values (a bin). E.g.,
participants read that John bought a watch.  To report their beliefs about the watch's price,
they adjust sliders whose endpoints are labelled as ``extremely likely'' and ``extremely
unlikely.'' Each slider corresponds to on out of 15 bins that partition the range of plausible
values (established by a pre-test), such as 0--50\$, 50--100\$, \dots 700--750\$. Each
subject's slider ratings are normalized within each item, and the results are averaged across
subjects to obtain an estimate of the population's average belief about each item. These
averaged normalized slider ratings per bin (henceforth: mean slider ratings) look intuitively
plausible and give good results if fed into cognitive models that predict behavior in language
or reasoning tasks, for instance.

>>>>

Another possibility is to empirically measure subjective beliefs by \emph{give-a-number}
tasks. The simplest version would be this: being told that John just bought a new watch,
subjects are asked for a single numerical estimate of its price. This task is easy to
comprehend and implement, but a single number does not provide much information about the
subjective belief that it is (arguably) a manifestation of. One solution is to infer which
parameterized distribution best explains the observed number choices, either at the individual
level \citep{Manski2004:Measuring-Expec} or on the population level
\citep{TauberSteyvers2013:Inferring-Subje}.

More sophisticated \emph{give-a-number} tasks give more information, but can be rather complex
and more difficult to implement. A prominent method in economics uses \emph{scoring rules}
\citep{Savage1971:Elicitation-of-,AndersenFountain2014:Estimating-Subj,SchlagTremewan2014:A-penny-for-you}. Roughly
put, scoring rules are schemes of rewarding participants' answers that make sure that responses
(by rational subjects) faithfully reflect a measure of interest: the actual subjective
probability of an event, the mean of a distribution, a credible interval etc. Scoring-rule
tasks require participants to become sufficiently familiar with the (usually probabilistic)
payoff scheme. Another insightful, but also complex approach is to use a cleverly designed
\emph{iterated learning paradigm} \citep{LewandowskyGriffiths2009:The-Wisdom-of-I}.

@@

A simple technique that seems to fit this bill is the \emph{binned histograms} task that has
recently been used with apparent success
\citep{KaoWu2014:Nonliteral-Unde,SchollerFranke2015:Semantic-values}. \mf{someone please add
  references: where did you use binned sliders?} Participants adjust sliders in order to
express their (relative) subjective beliefs about how likely it is that the value of an
uncertain contiguous quantity lies in some interval of possible values (a bin). E.g.,
participants read that John bought a watch.  To report their beliefs about the watch's price,
they adjust sliders whose endpoints are labelled as ``extremely likely'' and ``extremely
unlikely.'' Each slider corresponds to one out of 15 bins that partition the range of plausible
values (established by a pre-test). E.g., for the price of a watch bins could be ``\$0-\$50'',
``\$50-\$100'', etc. up to ``\$700-\$750'' and ``more than \$750''. Each subject's slider
ratings are normalized within each item, and the results are averaged across subjects to obtain
an estimate of the population's average belief about each item. These averaged normalized
slider ratings per bin (henceforth: mean slider ratings) look intuitively plausible and give
good results if fed into cognitive models that predict behavior in language or reasoning tasks,
for instance.
